%==============================================================================
% TEJO KASHYAP DIVI — Resume
% Target: Product Designer / Design Engineer
% ATS-optimized: single column, standard headings, no tables/columns/icons
%==============================================================================

\documentclass[11pt, letterpaper]{article}

\usepackage[
  top=0.45in,
  bottom=0.45in,
  left=0.6in,
  right=0.6in
]{geometry}

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\titleformat{\section}
  {\vspace{2pt}\bfseries\large}
  {}{0em}{}
  [\vspace{1pt}\titlerule\vspace{3pt}]

\setlist[itemize]{
  leftmargin=1.4em,
  itemsep=1pt,
  topsep=1pt,
  parsep=0pt
}

\hypersetup{colorlinks=true, urlcolor=black, hidelinks}

%==============================================================================
\begin{document}
%==============================================================================

%-- HEADER --------------------------------------------------------------------
\begin{center}
  {\LARGE \textbf{Tejo Kashyap Divi}}\\[5pt]
  Brooklyn, NY \quad|\quad
  +1 (929) 727-7912 \quad|\quad
  \href{mailto:divitejokashyap@gmail.com}{divitejokashyap@gmail.com}\\[2pt]
  \href{https://www.linkedin.com/in/divitejokashyap}{linkedin.com/in/divitejokashyap}
  \quad|\quad
  \href{https://tejokashyap.dev}{tejokashyap.dev}
\end{center}

%-- SUMMARY -------------------------------------------------------------------
\section{Summary}

Product Designer and Design Engineer with experience shipping production
interfaces at Deloitte and Amazon. I work across the full design-to-code
pipeline — research, Figma, and the React component that ends up in the
browser. Currently finishing an M.S. in Computer Science at NYU Tandon,
where I focus on the design of AI-facing systems. Looking for a full-time
Product Designer or Design Engineer role starting Summer 2026.

%-- EDUCATION -----------------------------------------------------------------
\section{Education}

\textbf{New York University, Tandon School of Engineering} \hfill Brooklyn, NY\\
M.S., Computer Science \hfill 2024 -- Present

\vspace{5pt}
\textbf{SRM Institute of Science and Technology} \hfill Chennai, India\\
B.Tech, Electrical and Electronics Engineering \hfill 2022

%-- EXPERIENCE ----------------------------------------------------------------
\section{Work Experience}

\textbf{Deloitte Consulting India Pvt Ltd} \hfill Hyderabad, India\\
\textit{Analyst, Frontend and UI} \hfill 2022 -- 2023

\begin{itemize}
  \item Owned the frontend of a customer-facing e-commerce platform from
        the first wireframe to the deployed build. Handled the HTML, CSS,
        Java, and Spring Boot, not just the design handoff.
  \item Designed and built the user authentication flow and product catalog
        from scratch, making decisions about information architecture and
        component structure that held up through two subsequent product
        iterations.
  \item Worked closely with the backend team to figure out why the database
        queries were choking under load, dug into the MySQL schema, and
        fixed the retrieval logic, a problem that had been sitting open
        for months.
  \item Presented design decisions and performance findings directly to
        client stakeholders, which taught me how to talk about interface
        choices to people who think in business outcomes, not pixels.
\end{itemize}

\vspace{6pt}
\textbf{Amazon} \hfill Hyderabad, India\\
\textit{DART Specialist} \hfill 2022

\begin{itemize}
  \item Got promoted to DART Specialist within the first six months, not a formal track but something I pushed toward by consistently
        taking on the cases nobody else wanted to touch.
  \item Handled manager-level escalations independently: diagnosed the
        underlying process failure, resolved it, and documented a fix so
        the same issue would not come back the same way twice.
  \item Started noticing patterns in the tickets that kept recurring and
        proposed workflow changes to the team lead that were eventually
        adopted across the floor.
  \item Built a personal system for triaging high-priority cases that a
        few colleagues started borrowing. My first real experience
        designing a process for people other than myself.
\end{itemize}

%-- PROJECTS ------------------------------------------------------------------
\section{Projects}

\textbf{Lume.Sys} — AI Observability Platform\\
\textit{React, TypeScript, Framer Motion, Figma} \hfill 2024

\begin{itemize}
  \item Built a monitoring dashboard for tracking inference requests across
        multiple language models simultaneously: latency trends, token
        usage, policy violations, and anomaly flags all in one view.
  \item Designed the information hierarchy from scratch: the hardest part
        was deciding what to suppress. Most observability tools show
        everything; this one surfaces what actually needs attention.
  \item Created the full component library in Figma and then implemented
        it in React, so nothing got lost in a handoff that never happened.
\end{itemize}

\vspace{5pt}
\textbf{Vault DS} — Enterprise Design System\\
\textit{React, TypeScript, Storybook, Design Tokens, Figma} \hfill 2024

\begin{itemize}
  \item Built a 128-component design system with a three-tier token
        architecture: Primitive, Semantic, and Component. The structure
        matters because it determines how easy the system is to theme
        and maintain six months later.
  \item Wrote every component in React and documented it in Storybook,
        including usage guidelines, prop tables, and accessibility notes
        -- the kind of documentation that actually gets read.
  \item Set up contribution guidelines and a versioning workflow, which
        forced me to think about design systems as infrastructure rather
        than just a component collection.
\end{itemize}

\vspace{5pt}
\textbf{Sync.Collab} — SaaS Collaboration Platform\\
\textit{Next.js 14, Supabase, TypeScript, Tailwind CSS, Figma} \hfill 2024

\begin{itemize}
  \item Designed and shipped a full-stack SaaS app in eight weeks: command
        palette, design review workflow, kanban board, real-time messaging,
        and a notification system.
  \item Started with user research and competitive analysis, moved through
        wireframes and a hi-fi Figma prototype, then built the whole thing
        in Next.js with Supabase handling auth and the database.
  \item The command palette was the feature I was most interested in, and it required thinking carefully about keyboard-first interaction
        patterns and progressive disclosure.
\end{itemize}

\vspace{5pt}
\textbf{Pulse Analytics} — Mobile Health Platform\\
\textit{Figma, React Native, Framer Motion} \hfill 2024

\begin{itemize}
  \item Designed a mobile wellness app for people who track biometrics
        seriously: recovery scores, sleep stages, HRV, habit stacking,
        and a 28-day trend view.
  \item The design problem was cognitive load: health apps usually throw
        everything at you. I focused the Today screen on a single recovery
        score with supporting context rather than a dashboard of equal-weight
        data points.
  \item Did user research with twelve people who use wearables regularly,
        ran concept testing on three different navigation patterns, and
        picked the one that people could use without thinking about it.
\end{itemize}

\vspace{5pt}
\textbf{Solo Leveling OS} — Gamified Productivity System\\
\textit{Next.js 14, Supabase, Claude API, Tailwind CSS} \hfill 2023 -- Present

\begin{itemize}
  \item A personal productivity app I built because every task manager
        I tried either had too much friction or not enough reason to open
        it again tomorrow. Built the gamification layer (XP, ranks, gate and mission structure) around actual habit research.
  \item Integrated the Claude API as an in-app assistant that can triage
        incoming thoughts, suggest which gate a task belongs to, and
        reflect back patterns in how I spend time.
  \item Full-stack and live: Next.js frontend, Supabase for auth and
        persistence, dark cyberpunk design system built entirely in Tailwind.
\end{itemize}

%-- SKILLS --------------------------------------------------------------------
\section{Skills}

\textbf{Design:}
Figma, User Research, Prototyping, Wireframing, Interaction Design,
Information Architecture, Design Systems, Design Tokens, WCAG Accessibility

\vspace{4pt}
\textbf{Design Engineering:}
React, Next.js, TypeScript, Tailwind CSS, Framer Motion, HTML, CSS,
Storybook, Component Libraries

\vspace{4pt}
\textbf{Backend and Data:}
Supabase, PostgreSQL, SQL, Java, Spring Boot, Python, REST APIs, Git

\vspace{4pt}
\textbf{AI and APIs:}
Claude API, Anthropic SDK, LLM integration, Prompt Engineering,
Hugging Face Transformers

\vspace{4pt}
\textbf{Tools:}
VS Code, GitHub, Vercel, Notion, Lovable.dev

%==============================================================================
\end{document}
%==============================================================================
